QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-11-22 Revision/Paper_Rev.tex
Rev_V9.1

In contrast to aformentationed related works \cite{zhang2023offline}--\cite{wu2023computation}, which overlook key performance metrics, we are motivated to effectively address QoE optimization, where QoE accounts for task completion rate, processing delay, and energy consumption. Different from \cite{zhang2023offline}--\cite{li2022integrated}, \cite{munir2021multi}--\cite{dai2020edge}, and \cite{liao2023online}--\cite{she2024efficient}, which considered delay-tolerant tasks, we take into account delay-sensitive tasks with processing deadlines. This is challenging to address, as processing deadlines impact the load dynamics at the ENs, which in turn affect the delay of offloaded tasks. 
  To effectively address personalized QoE optimization, we designed an adaptive balance for these factors according to the user's preferences, such as prioritizing reduced task delay or energy saving, which may vary over time. Each user may have unique QoE requirements at any given time.

>>>>

In contrast to the aforementioned related works \cite{zhang2023offline}--\cite{wu2023computation}, which neglect key performance aspects of user satisfaction, we are motivated to effectively address QoE optimization, where QoE accounts for task completion rate, processing delay, and energy consumption. 
  Specefically, different from \cite{zhang2023offline}--\cite{li2022integrated}, \cite{munir2021multi}--\cite{dai2020edge}, and \cite{liao2023online}--\cite{she2024efficient}, which considered delay-tolerant tasks, we take into account delay-sensitive tasks with processing deadlines. This is challenging to address, as processing deadlines impact the load dynamics at the ENs, which in turn affect the delay of offloaded tasks.
Although works \cite{gao2022large}--\cite{wu2023computation} taking these key performance factor into consideration, they fail to address user-specific demands. To effectively address personalized QoE optimization, we designed an adaptive balance for key QoE factors according to the dynamic user's individual preferences, such as prioritizing reduced task delay or energy saving, which may vary over time.
